Pipeline Performance Figure Generation

### 2023-05-29 TestingPipeline/Scripts/paper_figure_generation.Rmd
Visualizing change by adding tv.

>>>>

visualizing change when add the tnv rule
```{r}
accuracy_scores_one_ts <- accuracy_scores[accuracy_scores$testing_set_index==1,]

tnv <- rep(NA, 63)

for (i in 1:nrow(accuracy_scores_one_ts)) {
  tnv[i] <- as.numeric(substr(accuracy_scores_one_ts$toolcombo[i], 5, 5))
}

num_no_tnv <- 63-(sum(tnv))
```

```{r}
no_tnv_prop <- data.frame(tool_combo=accuracy_scores_one_ts$toolcombo[grep("0", tnv)],
                          prop_viral=rep(0, num_no_tnv),
                          MCC=rep(0, num_no_tnv),
                          precision=rep(0, num_no_tnv),
                          recall=rep(0, num_no_tnv))

tc_tnv <- "0"
tc_no_tnv <- "0"
prop_tnv <- 0
j <- 1

for (i in grep("0", tnv)) {
  tc_no_tnv <- as.character(accuracy_scores_one_ts$toolcombo[i])
  tc_tnv <- tc_no_tnv
  substr(tc_tnv, 5, 5) <- "1"

  prop_tnv <- accuracy_scores_one_ts$prop_viral[grep(tc_tnv,accuracy_scores_one_ts$toolcombo)][1]
  no_tnv_prop$prop_viral[j] <-
    (prop_tnv-accuracy_scores_one_ts$prop_viral[i])/prop_tnv*100

  prop_tnv <- accuracy_scores_one_ts$MCC[grep(tc_tnv,accuracy_scores_one_ts$toolcombo)][1]
  no_tnv_prop$MCC[j] <-
    (prop_tnv-accuracy_scores_one_ts$MCC[i])/prop_tnv*100

  prop_tnv <- accuracy_scores_one_ts$precision[grep(tc_tnv,accuracy_scores_one_ts$toolcombo)][1]
  no_tnv_prop$precision[j] <-
    (prop_tnv-accuracy_scores_one_ts$precision[i])/prop_tnv*100

  prop_tnv <- accuracy_scores_one_ts$recall[grep(tc_tnv,accuracy_scores_one_ts$toolcombo)][1]
  no_tnv_prop$recall[j] <-
    (prop_tnv-accuracy_scores_one_ts$recall[i])/prop_tnv*100

  j <- j+1
}

mean(no_tnv_prop$prop_viral)
sd(no_tnv_prop$prop_viral)

no_tnv_prop_melt <- no_tnv_prop %>% 
  select(precision, recall, MCC, prop_viral, tool_combo) %>%
  pivot_longer(cols=c(precision, recall, MCC, prop_viral), 
               names_to="performance_metric",
               values_to="performance_metric_percent_diff")

visualizing when add the tuning addition rule
```{r}
accuracy_scores_one_ts <- accuracy_scores[accuracy_scores$testing_set_index==1,]

tv <- rep(NA, 63)

for (i in 1:nrow(accuracy_scores_one_ts)) {
  tv[i] <- as.numeric(substr(accuracy_scores_one_ts$toolcombo[i], 1, 1))
}

num_no_tv <- 63-(sum(tv))

no_tv_prop <- data.frame(tool_combo=accuracy_scores_one_ts$toolcombo[grep("0", tv)],
                          prop_viral=rep(0, num_no_tv),
                          MCC=rep(0, num_no_tv),
                          precision=rep(0, num_no_tv),
                          recall=rep(0, num_no_tv))

tc_tv <- "0"
tc_no_tv <- "0"
prop_tv <- 0
j <- 1

for (i in grep("0", tv)) {
  tc_no_tv <- as.character(accuracy_scores_one_ts$toolcombo[i])
  tc_tv <- tc_no_tv
  substr(tc_tv, 1, 1) <- "1"

  prop_tv <- accuracy_scores_one_ts$prop_viral[grep(tc_tv,accuracy_scores_one_ts$toolcombo)][1]
  no_tv_prop$prop_viral[j] <-
    (prop_tv-accuracy_scores_one_ts$prop_viral[i])/prop_tv*100

  prop_tv <- accuracy_scores_one_ts$MCC[grep(tc_tv,accuracy_scores_one_ts$toolcombo)][1]
  no_tv_prop$MCC[j] <-
    (prop_tv-accuracy_scores_one_ts$MCC[i])/prop_tv*100

  prop_tv <- accuracy_scores_one_ts$precision[grep(tc_tv,accuracy_scores_one_ts$toolcombo)][1]
  no_tv_prop$precision[j] <-
    (prop_tv-accuracy_scores_one_ts$precision[i])/prop_tv*100

  prop_tv <- accuracy_scores_one_ts$recall[grep(tc_tv,accuracy_scores_one_ts$toolcombo)][1]
  no_tv_prop$recall[j] <-
    abs(prop_tv-accuracy_scores_one_ts$recall[i])/prop_tv*100

  j <- j+1
}

mean(no_tv_prop$prop_viral)
sd(no_tv_prop$prop_viral)

no_tv_prop_melt <- no_tv_prop %>% 
  select(precision, recall, MCC, prop_viral, tool_combo) %>%
  pivot_longer(cols=c(precision, recall, MCC, prop_viral), 
               names_to="performance_metric",
               values_to="performance_metric_percent_diff")
```

```{r}
no_tv_and_ntv_prop_melt <- rbind(no_tv_prop_melt, no_tnv_prop_melt)

no_tv_and_ntv_prop_melt$set <- c(rep("tuning addition", nrow(no_tv_prop_melt)),
                                 rep("tuning removal", nrow(no_tnv_prop_melt)))

pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")

fig <- ggplot(no_tv_and_ntv_prop_melt, 
              aes(x=performance_metric, y=performance_metric_percent_diff,
                  color=set, fill=set)) +
  geom_boxplot() +
  #geom_point() +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=10),
    axis.text.x=element_text(size=12),
    legend.text=element_text(size=12),
    axis.title=element_text(size=12),
    strip.background = element_rect(fill="white", color="grey"),
    strip.text = element_text(color="black", size=12)
  ) +
  xlab("Performance Metric") +
  ylab("Percent Difference") +
  geom_hline(yintercept = 1, color="grey") +
  scale_fill_manual(name="",
                     values = alpha(c(pal(6)[c(6,1)]), 0.4)) +
  scale_color_manual(name="",
                     values = alpha(c(pal(6)[c(6,1)]), 0.6))
